Kids health and child data cleaning

### 2020-04-22 child_health_data_cleaning.Rmd
health data cleaning

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 20 April 2020"
output: pdf_document 
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
demographics_clean <- 
  read_rds(paste0(file_path, "Output/demographics_clean.rds"))
pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))
```

@@

# write_rds(kids_at_home_log, "Output/kids_at_home_log.rds")
```

@@

# Load and merge files from different locations
```{r}
wmt_medicalvisit_initial <- read_xlsx("Input/WMT/wmt_medicalvisit_20200227.xlsx") %>% 
  mutate(HRPulseOx = if_else(HRPulseOx < 50, -999, HRPulseOx),
         HR = if_else(HR < 50, -999, HR),
         SP02 = if_else(SP02 < 70, -999, SP02)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-999, -9999, 0)) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         med_visit_lethargy = as.character(Lethargy),
         med_visit_retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         med_visit_resp_rate = as.numeric(RR),
         med_visit_heart_rate = as.numeric(HR),
         med_visit_wheeze = as.character(Wheeze),
         med_visit_stridor = as.character(Stridor),
         med_visit_crackles = as.character(Crackles),
         med_visit_sp02 = as.numeric(SP02),
         med_visit_hr_sp02 = as.numeric(HRPulseOx),
         med_visit_referred = as.character(Referred),
         med_visit_notes = as.character(Level)) %>% 
  # gather 3 temperatures to calculate average
  gather("sample", "value", c("temp1":"temp3")) %>% 
  group_by(home_winter_id, child_id_num, med_visit_date) %>% 
  mutate(value = if_else(value < 90, -99, value)) %>% 
  replace_with_na(replace = list(value = -99)) %>% 
  mutate(med_visit_mean_temp = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>%
  select(home_winter_id:med_visit_mean_temp)

@@

# Load and merge files from different locations
```{r}
wmt_birthinfancy_initial <- read_xlsx(paste0(file_path, "Input/WMT/wmt_birthinfancy_20200227.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         gender = as.character(Gender),
         bw_lbs = as.numeric(BirthweightLbs),
         bw_oz = as.numeric(BirthWeightOz),
         birth_weight_oz = as.numeric((bw_lbs*16)+bw_oz),
         mom_age = as.numeric(AgeOfMom),
         breastfeed_current = as.character(CurrentlyBreastfeeding),
         breastfeed_past = as.character(DidBreastfeed),
         bf_years = as.numeric(HowLongYears),
         bf_months = as.numeric(HowLongMonths),
         breastfeed_months = as.numeric((bf_years*12)+bf_months),
         flu_shot = as.character(FluShot),
         flu_shot_planned = as.character(FluShotPlanned),
         asthma_meds = as.character(AsthmaMeds),
         child_school = as.character(Attend),
         school_hours = as.numeric(HoursDay),
         school_days = as.numeric(DaysWeek),
         school_hours_week = as.numeric(school_hours*school_days),
         sibling_school = as.character(SibSchool)) %>% 
  select(home_winter_id:sibling_school)

nn_birthinfancy_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_birthinfancy_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         gender = as.character(Gender),
         bw_lbs = as.numeric(BirthweightLbs),
         bw_oz = as.numeric(BirthWeightOz),
         birth_weight_oz = as.numeric((bw_lbs*16)+bw_oz),
         mom_age = as.numeric(AgeOfMom),
         breastfeed_current = as.character(CurrentlyBreastfeeding),
         breastfeed_past = as.character(DidBreastfeed),
         bf_years = as.numeric(HowLongYears),
         bf_months = as.numeric(HowLongMonths),
         breastfeed_months = as.numeric((bf_years*12)+bf_months),
         flu_shot = as.character(FluShot),
         flu_shot_planned = as.character(FluShotPlanned),
         asthma_meds = as.character(AsthmaMeds),
         child_school = as.character(Attend),
         school_hours = as.numeric(HoursDay),
         school_days = as.numeric(DaysWeek),
         school_hours_week = as.numeric(school_hours*school_days),
         sibling_school = as.character(SibSchool)) %>% 
  select(home_winter_id:sibling_school)

ak_birthinfancy_initial <- read_xlsx(paste0(file_path, "Input/AK/ak_birthinfancy_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "AK",
         gender = as.character(Gender),
         bw_lbs = as.numeric(BirthweightLbs),
         bw_oz = as.numeric(BirthWeightOz),
         birth_weight_oz = as.numeric((bw_lbs*16)+bw_oz),
         mom_age = as.numeric(AgeOfMom),
         breastfeed_current = as.character(CurrentlyBreastfeeding),
         breastfeed_past = as.character(DidBreastfeed),
         bf_years = as.numeric(HowLongYears),
         bf_months = as.numeric(HowLongMonths),
         breastfeed_months = as.numeric((bf_years*12)+bf_months),
         flu_shot = as.character(FluShot),
         flu_shot_planned = as.character(FluShotPlanned),
         asthma_meds = as.character(AsthmaMeds),
         child_school = as.character(Attend),
         school_hours = as.numeric(HoursDay),
         school_days = as.numeric(DaysWeek),
         school_hours_week = as.numeric(school_hours*school_days),
         sibling_school = as.character(SibSchool)) %>% 
  select(home_winter_id:sibling_school)

@@

# Load and merge files from different locations
```{r}
wmt_childhomewinter_initial <- 
  read_xlsx(paste0(file_path, "Input/WMT/wmt_childhomewinter_20200227.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         chw_dr_relook = DrRelook,
         chw_ari_status = as.character(Status),
         chw_symptom_free_date = ymd(SymptomFreeDate),
         chw_csq_duedate = ymd(CSQDueDate),
         chw_csq_date = ymd(CSQDate),
         chw_csq_time = as.character(CSQTime),
         chw_dr_comments = as.character(DrComments),
         chw_dr_history = as.character(DrHistory),
         chw_notify_parents = as.character(NotifyParents),
         chw_notes_to_parents = as.character(NotesToParents),
         chw_any_ari = as.character(AnyARI),
         chw_ari_comments = as.character(WinterARIComments)) %>% 
  select(home_winter_id:chw_ari_comments)

@@

nn_csq_initial <- 
  read_xlsx(paste0(file_path, "Input/NN/nn_csq_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         csq_date = ymd(Date),
         csq_collect = as.character(HowCollected),
         csq_sick_2_weeks = as.character(Illin2Weeks),
         csq_still_sick = as.character(StillSick),
         csq_first_symptom_date = ymd(FirstSymptomDate),
         csq_symptom_free_date = ymd(SymptomFreeDate),
         csq_miss_work = as.character(MissWork),
         csq_miss_work_days = as.character(DaysMissed),
         csq_see_dr = as.character(SeeDr),
         csq_dr_diagnosis = as.character(DrDiagnosis),
         csq_new_meds = as.character(NewMeds),
         csq_fever_2weeks = as.character(Fever),
         csq_temp_2weeks = as.numeric(Temperature),
         csq_rapid_breathing_2weeks = as.character(RapidBreathing),
         csq_difficult_breathing_2weeks = as.character(DifficultBreathing),
         csq_noisy_breathing_2weeks = as.character(NoisyBreathing),
         csq_runny_nose_2weeks = as.character(RunnyNose),
         csq_cough_2weeks = as.character(Coughing),
         csq_wheeze_2weeks = as.character(Wheezing),
         csq_fever_current = as.character(FeverStill),
         csq_rapid_breathing_current = as.character(RapidBreathingStill),
         csq_difficult_breathing_current = as.character(DifficultBreathingStill),
         csq_noisy_breathing_current = as.character(NoisyBreathingStill),
         csq_runny_nose_current = as.character(RunnyNoseStill),
         csq_cough_current = as.character(CoughingStill),
         csq_wheeze_current = as.character(WheezingStill),
         csq_comments = as.character(`REPLACE(REPLACE(Comments, '\\n', ''), '\\r', '')`)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-999, -99, -99.9, 999, 0)) %>% 
  select(home_winter_id:csq_comments)

@@

# write_rds(kids_csq, "Output/kids_csq.rds")

@@

# Load and merge files from different locations
```{r}
wmt_medicalrecords_initial <- 
  read_xlsx(paste0(file_path, "Input/WMT/wmt_medicalrecords_20200227.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(ARI),
         med_rec_comments = as.character(DrComments)) %>% 
  select(home_winter_id:med_rec_comments)

nn_medicalrecords_initial <- 
  read_xlsx(paste0(file_path, "Input/NN/nn_medicalrecords_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(ARI),
         med_rec_comments = as.character(DrComments)) %>% 
  select(home_winter_id:med_rec_comments)

ak_medicalrecords_initial <- 
  read_xlsx(paste0(file_path, "Input/AK/ak_medicalrecords_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "AK",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(ARI),
         med_rec_comments = as.character(DrComments)) %>% 
  select(home_winter_id:med_rec_comments)

# Combine logs from all areas
kids_medical_records <- wmt_medicalrecords_initial %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

@@

# Load and merge files from different locations
```{r}
wmt_ari_initial <- read_xlsx("Input/WMT/wmt_ari_20200408.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         lrti_number = as.character(ARINum),
         lrti_basis = as.character(ARIBasis),
         lrti_start_date_final = ymd(ProfessionalStartDate),
         lrti_end_date_final = ymd(ProfessionalEndDate),
         lrti_professional_comments = as.character(ProfessionalComments)) %>% 
  select(home_winter_id:lrti_professional_comments)

>>>>

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 22 April 2020"
output: pdf_document 
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
```

@@

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

demographics_clean <- 
  read_rds(paste0(file_path, "Output/demographics_clean.rds"))

pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))
```

@@

# write_rds(kids_at_home_log, paste0(file_path, "Output/kids_at_home_log.rds"))
```

@@

# Load and merge files from different locations
```{r}
wmt_medicalvisit_initial <- read_xlsx(paste0(file_path, "Input/WMT/wmt_medicalvisit_20200227.xlsx")) %>% 
  mutate(HRPulseOx = if_else(HRPulseOx < 50, -999, HRPulseOx),
         HR = if_else(HR < 50, -999, HR),
         SP02 = if_else(SP02 < 70, -999, SP02)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-999, -9999, 0)) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         med_visit_date = ymd(VisitDate),
         med_visit_ari = as.character(ARI),
         med_visit_lethargy = as.character(Lethargy),
         med_visit_retractions = as.character(Retractions),
         temp1 = as.numeric(Temp1),
         temp2 = as.numeric(Temp2),
         temp3 = as.numeric(Temp3),
         med_visit_resp_rate = as.numeric(RR),
         med_visit_heart_rate = as.numeric(HR),
         med_visit_wheeze = as.character(Wheeze),
         med_visit_stridor = as.character(Stridor),
         med_visit_crackles = as.character(Crackles),
         med_visit_sp02 = as.numeric(SP02),
         med_visit_hr_sp02 = as.numeric(HRPulseOx),
         med_visit_referred = as.character(Referred),
         med_visit_notes = as.character(Level)) %>% 
  # gather 3 temperatures to calculate average
  gather("sample", "value", c("temp1":"temp3")) %>% 
  group_by(home_winter_id, child_id_num, med_visit_date) %>% 
  mutate(value = if_else(value < 90, -99, value)) %>% 
  replace_with_na(replace = list(value = -99)) %>% 
  mutate(med_visit_mean_temp = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>%
  select(home_winter_id:med_visit_mean_temp)

@@

# Load and merge files from different locations
```{r}
wmt_birthinfancy_initial <- read_xlsx(paste0(file_path, "Input/WMT/wmt_birthinfancy_20200227.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         gender = as.character(Gender),
         bw_lbs = as.numeric(BirthweightLbs),
         bw_oz = as.numeric(BirthWeightOz),
         birth_weight_oz = as.numeric((bw_lbs*16)+bw_oz),
         mom_age = as.numeric(AgeOfMom),
         breastfeed_current = as.character(CurrentlyBreastfeeding),
         breastfeed_past = as.character(DidBreastfeed),
         bf_years = as.numeric(HowLongYears),
         bf_months = as.numeric(HowLongMonths),
         breastfeed_months = as.numeric((bf_years*12)+bf_months),
         flu_shot = as.character(FluShot),
         flu_shot_planned = as.character(FluShotPlanned),
         asthma_meds = as.character(AsthmaMeds),
         child_school = as.character(Attend),
         school_hours = as.numeric(HoursDay),
         school_days = as.numeric(DaysWeek),
         school_hours_week = as.numeric(school_hours*school_days),
         sibling_school = as.character(SibSchool)) %>% 
  replace_with_na(replace = list(bw_lbs = 0, birth_weight_oz = 0, mom_age = 0)) %>%
  select(home_winter_id:sibling_school)

nn_birthinfancy_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_birthinfancy_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         gender = as.character(Gender),
         bw_lbs = as.numeric(BirthweightLbs),
         bw_oz = as.numeric(BirthWeightOz),
         birth_weight_oz = as.numeric((bw_lbs*16)+bw_oz),
         mom_age = as.numeric(AgeOfMom),
         breastfeed_current = as.character(CurrentlyBreastfeeding),
         breastfeed_past = as.character(DidBreastfeed),
         bf_years = as.numeric(HowLongYears),
         bf_months = as.numeric(HowLongMonths),
         breastfeed_months = as.numeric((bf_years*12)+bf_months),
         flu_shot = as.character(FluShot),
         flu_shot_planned = as.character(FluShotPlanned),
         asthma_meds = as.character(AsthmaMeds),
         child_school = as.character(Attend),
         school_hours = as.numeric(HoursDay),
         school_days = as.numeric(DaysWeek),
         school_hours_week = as.numeric(school_hours*school_days),
         sibling_school = as.character(SibSchool)) %>% 
  replace_with_na(replace = list(bw_lbs = 0, birth_weight_oz = 0, mom_age = 0)) %>%
  select(home_winter_id:sibling_school)

ak_birthinfancy_initial <- read_xlsx(paste0(file_path, "Input/AK/ak_birthinfancy_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "AK",
         gender = as.character(Gender),
         bw_lbs = as.numeric(BirthweightLbs),
         bw_oz = as.numeric(BirthWeightOz),
         birth_weight_oz = as.numeric((bw_lbs*16)+bw_oz),
         mom_age = as.numeric(AgeOfMom),
         breastfeed_current = as.character(CurrentlyBreastfeeding),
         breastfeed_past = as.character(DidBreastfeed),
         bf_years = as.numeric(HowLongYears),
         bf_months = as.numeric(HowLongMonths),
         breastfeed_months = as.numeric((bf_years*12)+bf_months),
         flu_shot = as.character(FluShot),
         flu_shot_planned = as.character(FluShotPlanned),
         asthma_meds = as.character(AsthmaMeds),
         child_school = as.character(Attend),
         school_hours = as.numeric(HoursDay),
         school_days = as.numeric(DaysWeek),
         school_hours_week = as.numeric(school_hours*school_days),
         sibling_school = as.character(SibSchool)) %>% 
  replace_with_na(replace = list(bw_lbs = 0, birth_weight_oz = 0, mom_age = 0)) %>% 
  select(home_winter_id:sibling_school)

@@

As of 22 April 2020 we only have CHW files for WMT.
The content isn't particularly necessary for data analysis, so leave out of the
final dataset for now and see if files for NN and AK come up later.
```{r}
wmt_childhomewinter_initial <- 
  read_xlsx(paste0(file_path, "Input/WMT/wmt_childhomewinter_20200227.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         chw_dr_relook = DrRelook,
         chw_ari_status = as.character(Status),
         chw_symptom_free_date = ymd(SymptomFreeDate),
         chw_csq_duedate = ymd(CSQDueDate),
         chw_csq_date = ymd(CSQDate),
         chw_csq_time = as.character(CSQTime),
         chw_dr_comments = as.character(DrComments),
         chw_dr_history = as.character(DrHistory),
         chw_notify_parents = as.character(NotifyParents),
         chw_notes_to_parents = as.character(NotesToParents),
         chw_any_ari = as.character(AnyARI),
         chw_ari_comments = as.character(WinterARIComments)) %>% 
  select(home_winter_id:chw_ari_comments)

@@

nn_csq_initial <- 
  read_xlsx(paste0(file_path, "Input/NN/nn_csq_20200416.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         csq_date = ymd(Date),
         csq_collect = as.character(HowCollected),
         csq_sick_2_weeks = as.character(Illin2Weeks),
         csq_still_sick = as.character(StillSick),
         csq_first_symptom_date = ymd(FirstSymptomDate),
         csq_symptom_free_date = ymd(SymptomFreeDate),
         csq_miss_work = as.character(MissWork),
         csq_miss_work_days = as.character(DaysMissed),
         csq_see_dr = as.character(SeeDr),
         csq_dr_diagnosis = as.character(DrDiagnosis),
         csq_new_meds = as.character(NewMeds),
         csq_fever_2weeks = as.character(Fever),
         csq_temp_2weeks = as.numeric(Temperature),
         csq_rapid_breathing_2weeks = as.character(RapidBreathing),
         csq_difficult_breathing_2weeks = as.character(DifficultBreathing),
         csq_noisy_breathing_2weeks = as.character(NoisyBreathing),
         csq_runny_nose_2weeks = as.character(RunnyNose),
         csq_cough_2weeks = as.character(Coughing),
         csq_wheeze_2weeks = as.character(Wheezing),
         csq_fever_current = as.character(FeverStill),
         csq_rapid_breathing_current = as.character(RapidBreathingStill),
         csq_difficult_breathing_current = as.character(DifficultBreathingStill),
         csq_noisy_breathing_current = as.character(NoisyBreathingStill),
         csq_runny_nose_current = as.character(RunnyNoseStill),
         csq_cough_current = as.character(CoughingStill),
         csq_wheeze_current = as.character(WheezingStill),
         csq_comments = as.character(`REPLACE(REPLACE(Comments, '\\n', ''), '\\r', '')`)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-9999, -999, -99, -99.9, 999, 0)) %>% 
  select(home_winter_id:csq_comments)

@@

# write_rds(kids_csq, paste0(file_path, "Output/kids_csq.rds"))

@@

These files are different for WMT compared to NN and AK
The relevant information from NN/AK med recs seems to be in the "respiratory" 
file. For now, I'll read those in and match with the WMT med rec file.

See if WMT file for med rec/respiratory is updated once all data is input.
```{r}
wmt_medicalrecords_initial <- 
  read_xlsx(paste0(file_path, "Input/WMT/wmt_medicalrecords_20200227.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(ARI),
         med_rec_comments = as.character(DrComments),
         med_rec_meds = "NA",
         med_rec_tests = "NA",
         med_rec_treatments = "NA",
         med_rec_chart_notes = "NA") %>% 
  select(home_winter_id:med_rec_chart_notes)

nn_medicalrecords_initial <- 
  read_xlsx(paste0(file_path, "Input/NN/nn_respiratory_20200416.xlsx"),
            skip = 1,
            col_names = c("id", "mrid", "ChildID", "HomeWinterID", "VisitDate",
                          "DrDiag", "tests", "treatments", "meds", "Status",
                          "DrComments"),
            col_types = c("numeric", "numeric", "text", "text", "date",
                          "text", "text", "text", "text",
                          "text", "text")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "NN",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(Status),
         med_rec_comments = as.character(DrComments),
         med_rec_meds = as.character(meds),
         med_rec_tests = as.character(tests),
         med_rec_treatments = as.character(treatments),
         med_rec_chart_notes = "NA") %>% 
  select(home_winter_id:med_rec_chart_notes)

ak_medicalrecords_initial <- 
  read_xlsx(paste0(file_path, "Input/AK/ak_respiratory_20200416.xlsx"),
            skip = 1,
            col_names = c("id", "mrid", "ChildID", "HomeWinterID", "VisitDate",
                          "DrDiag", "tests", "treatments", "meds", 
                          "chartnotes", "prestudy", "Status",
                          "DrComments"),
            col_types = c("numeric", "numeric", "text", "text", "date",
                          "text", "text", "text", "text", "text", "text",
                          "text", "text")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "AK",
         visit_date = ymd(VisitDate),
         med_rec_visit_date = ymd(VisitDate),
         med_rec_dr_diagnosis = as.character(DrDiag),
         med_rec_ari = as.character(Status),
         med_rec_comments = as.character(DrComments),
         med_rec_meds = as.character(meds),
         med_rec_tests = as.character(tests),
         med_rec_treatments = as.character(treatments),
         med_rec_chart_notes = as.character(chartnotes)) %>% 
  select(home_winter_id:med_rec_chart_notes)

# Combine logs from all areas
kids_medical_records <- rbind(wmt_medicalrecords_initial, nn_medicalrecords_initial,
                              ak_medicalrecords_initial) %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id")) %>% 
  arrange(area, visit_date)

@@

There isn't an LRTI file for NN/AK as of 22 April 2020. 
Leaving WMT file for now and will check back on updated data/files later.
```{r}
wmt_ari_initial <- read_xlsx("Input/WMT/wmt_ari_20200408.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         lrti_number = as.character(ARINum),
         lrti_basis = as.character(ARIBasis),
         lrti_start_date_final = ymd(ProfessionalStartDate),
         lrti_end_date_final = ymd(ProfessionalEndDate),
         lrti_professional_comments = as.character(ProfessionalComments)) %>% 
  select(home_winter_id:lrti_professional_comments)
